The imprint of global magma oceans on exoplanet demographics

### 2022-11-23 src/tex/ms.tex
map conclusions back to Discussion section

\section{Testing the magma ocean hypothesis}
\todo[inline]{"Methods Section" of the hypothesis testing part. Introduce the idea of constraining magma ocean frequencies and/or physics with Bayesian stats on exoplanet population; introduce Bioverse; report methods of the hypothesis tests.}

@@

\subsection{Signature and testability of the magma ocean hypothesis with a $<nominal telescope size>$ class space telescope survey}

@@

\section{Discussion}\label{sec:discussion}
\todo[inline]{\textbf{Potential discussion points: } what is the fraction of Kepler planets w/ runaway GH.}

@@

\subsection{Atmospheric signatures}
\todo[inline]{discuss potential atmospheric signatures of magma oceans. e.g.: H/O ratios of sub-Neptunes could be low (because H is in the melt) (Tim's talk)}

@@

\subsection{Mission design trades}\label{sec:mission-design-trades}
\todo[inline]{Maps to Sect. \ref{sec:statpower_missions}.}

>>>>

\section{Testing the magma ocean hypothesis}
\todo[inline]{Methods and results section of the hypothesis testing part. Introduce the idea of constraining magma ocean frequencies and/or physics with Bayesian stats on exoplanet population; introduce Bioverse; report methods of the hypothesis tests.}

@@

\subsection{Signature and testability of the magma ocean hypothesis with the PLATO transit survey}

@@

\section{Discussion}\label{sec:discussion}
\todo[inline]{\textbf{Potential discussion points: } what is the fraction of Kepler planets w/ runaway GH.}
\subsection{Expected imprint of runaway greenhouse phases on exoplanet demographics}

\subsection{Detectability of the magma ocean demographic feature}

\subsection{Diagnostic power of upcoming exoplanet missions}\todo[inline]{PLATO: needed sample size, precision}

\subsection{Mission design trades}\label{sec:mission-design-trades}

@@

\subsection{OPTIONAL...: Atmospheric signatures}
\todo[inline]{discuss potential atmospheric signatures of magma oceans. e.g.: H/O ratios of sub-Neptunes could be low (because H is in the melt) (Tim's talk)}

@@

\todo[inline]{Maps to Sect. \ref{sec:statpower_missions}.}
